\documentclass[11pt]{article}
\usepackage[margin= 0.5 in]{geometry}
\usepackage{hyperref}
\usepackage{fix-cm}
\pagenumbering{gobble}
\normalsize

% resume header details 
\newcommand{\selfName}{\textbf{\fontsize{30}{30}\selectfont JEAN SUNG }}
\newcommand{\email}{\large {jeansung94@gmail.com }}
\newcommand{\phone}{\large (206)-734-5538 }
\newcommand{\tildeText}{\raise.17ex\hbox{$\scriptstyle\sim$}}
\newcommand{\websitedisplaytext}{\large jeansung.github.io }
\newcommand{\website}{\href{http://jeansung.github.io}{\websitedisplaytext}}
\newcommand{\wrapTitle}[1]{{\textbf{\sectionNL \Large #1}} \sectionNL}


% shortcuts 
\newcommand{\headerdot}{  $\bullet$  }
\newcommand{\vb}{ $\mid$ }
\newcommand{\sectionNL}{~\\[0.5pt]}
\newcommand{\customtab}{$\hspace{10pt} \bullet \hspace{2pt}$}
\newcommand{\customtabinline}{$\hspace{23pt}$}
\newcommand{\HMC}{HMC}
\newcommand{\JudgeNudge}{\hspace{4pt}}
\newcommand{\rightAlign}{\hfill}

\begin{document}
% Contact Information 
\begin{center}
\selfName\\
\phone  
\vb\email 
\vb\website \\
\hrulefill
\end{center}


% Education
\begin{flushleft}
\wrapTitle{EDUCATION}
Harvey Mudd College (\HMC), Claremont, CA \rightAlign \textbf{May 2016 } \\
B.S. Computer Science, Graduated with Distinction - Major GPA: 3.5 \\
Harvey S. Mudd Merit Award (2012-2016), Dean's List (2014-2016)
\end{flushleft}

% Coursework
\begin{flushleft}
\wrapTitle{SELECTED COURSEWORK}
Advanced Algorithms
\vb Domain Specific Languages 
\vb Data Structures  
\vb Interaction Design
\vb Public Speaking \\
Digital Electronics \& Computer Engineering
\vb Linear Algebra \& Differential Equations  
\vb Discrete Mathematics
\end{flushleft}

\begin{flushleft}
{\sectionNL \Large \textbf{SKILLS:}}
Python 
\vb Java 
\vb C++
\vb Bash
\vb \LaTeX
\vb MATLAB
\vb Git
\vb SVN
\end{flushleft}

% Experience
\begin{flushleft}
\wrapTitle{EXPERIENCE}
\textbf{Software Engineer @ Facebook}, Seattle, WA \rightAlign \textbf{Starting Aug. 2016} \\
\textbf{Algorithms Researcher}, HMC \rightAlign \textbf{May 2016 - July 2016} \\
\customtab Worked on approximation bounds and clustering algorithms for the reconciliation of phylogenetic trees \\
\customtab Submitted \textit{Clustering Algorithms for Maximum Parsimony DTL Reconciliations} to  a journal for review  \\
\textbf{Software Engineering Intern @ zulily}, Seattle WA \rightAlign \textbf{June 2015 - Aug. 2015} \\
\customtab Conducted feasibility research on a price prediction model that resulted in saved company resources \\
\customtab Designed, implemented, tracked results for several experiments involving novel ways of arranging the site \\
\end{flushleft}

\begin{flushleft}
\wrapTitle{PROJECTS}
\textbf{Model Driving Creation} (\url{https://github.com/jeansung/MDReadWrite}) \rightAlign \textbf{Jan. 2016 - May 2016} \\
\customtab Creating an application to embed simple math models in text documents with an interactive component \\
\customtab Wrote a wrapper for Tangle JS library to increase usability by non programmers \\

\textbf{Sum Plus Plus} (\url{http://jeansung.github.io/SumPlusPlus/}) \rightAlign \textbf{Sept. 2014 - Dec. 2014} \\
\customtab Created a domain specific language to more cleanly express weighed sums with custom constraints \\
\customtab Designed a translation suite for English rules to Excel formulas \\

\textbf{Pipe Dream!} (\url{https://itunes.apple.com/us/app/pipe-dream!/id947630499})  \rightAlign \textbf{Sept. 2014 - Dec. 2014} \\
\customtab Created an educational iPad game to teach middle school students about computer security\\
\customtab Gained experience in agile development process, teamwork, architecture design and user testing \\
\customtab Winner of the 2015 Computer Science Dept. Wing Tam Award for Best Software Development Project 
\end{flushleft}


\begin{flushleft}
\wrapTitle{SERVICE}
\textbf{STEAM Coders Lead Instructor} \rightAlign \textbf{June 2016 - July 2016} \\
\customtab Taught programming and computing fundamentals to \tildeText20 5th-8th grade students  \\
\customtab Coordinated logistics of briefing \tildeText10 volunteers, acquiring materials and securing a space \\
\textbf{Girls Who Code Lead Instructor} \rightAlign \textbf{Dec. 2014 - May 2016} \\
\customtab Created curriculum for teaching Scratch and basic computer science principles \\
\customtab Taught Scratch and Python (using Codesters learning platform) to middle school girls \\
\customtab Introduced greedy algorithms, divide and conquer and proof by induction\\
\textbf{Computer Science Grader \& Tutor} \rightAlign \textbf{Sept. 2013 - May 2016} \\
\customtab Assisted in Algorithms, Domain Specific Languages (DSLs), Data Structures, Software Development   \\
\customtab For DSLs, worked directly with professor to improve grading procedures and processes\
\end{flushleft}

\end{document}